Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-08-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
replace spectrum by range

A potential limiting factor in this study could be the upper limit of 600 iterations used for the XGBoost algorithm (hyperparameter \texttt{nrounds}), especially for feature sets including NRIs (\autoref{tab:hyperparameter_limits}).
This setting was a compromise between runtime and tuning space extension with the goal to work well for most feature sets.
It may be recommendable to increase this upper limit to a value closer to the number of features in the dataset in order to be able to exploit the full spectrum of this hyperparameter.

>>>>

A potential limiting factor in this study could be the upper limit of 600 iterations used for the XGBoost algorithm (hyperparameter \texttt{nrounds}), especially for feature sets including NRIs (\autoref{tab:hyperparameter_limits}).
This setting was a compromise between runtime and tuning space extension with the goal to work well for most feature sets.
It may be recommendable to increase this upper limit to a value closer to the number of features in the dataset in order to be able to exploit the full range of this hyperparameter.
